Distance distribution by modes

### 2019-08-07 code/trips_analysis/trip_distance.Rmd

>>>>

## Trip distance - histogram

```{r genTotalHistPlots, message = T, echo = F, warning = F}

rd1 <- io$accra$trip_scen_sets %>% mutate(cs = 'Accra') %>% select(cs, trip_distance, trip_distance_cat)
rd2 <- io$sao_paulo$trip_scen_sets %>% mutate(cs = 'Sao Paulo') %>% select(cs, trip_distance, trip_distance_cat)
rd3 <- io$delhi$trip_scen_sets %>% mutate(cs = 'Delhi') %>% select(cs, trip_distance, trip_distance_cat)

rd <- plyr::rbind.fill(rd1, rd2, rd3)

op <- ggplot(rd %>% filter(trip_distance < 51)) +
  aes(x = trip_distance, fill = cs) +
  geom_histogram(breaks = c(0:10,seq(11, 51, by = 5)), alpha=0.8, position="identity", aes(y = ..density..)) +
  labs(x = '') + 
  #geom_density(alpha = 0.4, color = 'lightgrey') +
  facet_wrap(vars(cs))

ggplotly(op)

## Trip distance - density

```{r genTotalDensityPlots, message = T, echo = F, warning = F}

op <- ggplot(rd %>% filter(trip_distance < 50)) +
  aes(x = trip_distance, fill = cs) +
  labs(x = '') + 
  #geom_histogram(breaks = c(0:10,seq(11, 61, by = 5)), alpha=0.8, position="identity", aes(y = ..density..)) +
  geom_density(alpha = 0.8) +
  facet_wrap(vars(cs))

ggplotly(op)
